---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Sijia Gao



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE
cces$ideo5 <- recode(cces$ideo5, `1`="Very Liberal", `2`="Liberal", `3`="Moderate", `4`="Conservative", `5`="Very Conservative")

ggplot(data = cces, aes(x=ideo5, fill=ideo5)) +
  geom_bar(stat = "count") +
  xlab("Ideology") + ylab("Count") + 
  ggtitle("Respondent Ideology") + 
  guides(fill=FALSE)

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE
cces$pew_religimp <- recode(cces$pew_religimp, `1`="Very imp.", `2`="Somewhat imp.", `3`="Not too imp.", `4`="Not imp.")
cces <- cces %>% rename(Ideology=ideo5)

ggplot(data=cces, aes(x=pew_religimp, fill=Ideology)) +
  geom_bar() + 
  xlab("Importance of Religion") + ylab("Count") +
  ggtitle("Importance of Religion by Ideology")

```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE
stu = c("Amanda", "Betty", "Carol")
sem = seq(1,6)
data <- expand.grid(Student=stu, Semester=sem)
data$Grade = runif(18,80,100)

ggplot(data, aes(x=Semester, y=Grade, fill=Student, color=Student)) +
  geom_line(linetype = "solid", size = 1) + 
  ggtitle("Student Grades by Semester") + 
  facet_wrap(~Student) + 
  guides(fill=FALSE, color=FALSE)

```
